### 2021-01-02 treatise-pdflatex/foreword.tex
Front matter passes compilation

\starttitle [title={Foreword}]

@@

The present treatise is far from being remarkable, but I suppose the course of devising, clarifying, speculating, verifying, programming, debugging, googling, and polishing does teach some resilience to a weak mind.
The three and half years are punctuated by Bāchí martial art practice session, teaching assistant's preparation and scoring, chess club meeting, MediaTek internship, and the two semester courses of Real Analysis and Advanced Statistical Inference, which are recollections I too hold dearly.

@@

\stoptitle

>>>>

\chapter* {Foreword}

@@

The present treatise is far from being remarkable, but I suppose the course of devising, clarifying, speculating, verifying, programming, debugging, googling, and polishing does teach some resilience to a weak mind.
The three and half years are punctuated by Bachi martial art practice session, teaching assistant's preparation and scoring, chess club meeting, MediaTek internship, and the two semester courses of Real Analysis and Advanced Statistical Inference, which are recollections I too hold dearly.

@@
